%
% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}

%
% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

\include{psd-macros}
%\include{psd-macros-extra}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{colortbl}
\usepackage{xcolor}
\usepackage{subcaption}

\usepackage[boxed,linesnumbered,lined,commentsnumbered]{algorithm2e}


% track is a boolean variable if we should track changes (manual)
\newtoggle{track}
\toggletrue{track}
%\togglefalse{track}
\iftoggle{track}
{
\newcommand{\new}[1]{\textcolor{red}{#1}}
\newcommand{\old}[1]{\textcolor{blue}{\textbf{\st{#1}}}}
}
{
\newcommand{\new}[1]{#1}
\newcommand{\old}[1]{}
}

% Rights management information. 
% This information is sent to you when you complete the rights form.
% These commands have SAMPLE values in them; it is your responsibility as an author to replace
% the commands and values with those provided to you when you complete the rights form.
%
% These commands are for a PROCEEDINGS abstract or paper.
\copyrightyear{2019}
\acmYear{2019}
\setcopyright{acmlicensed}
\acmConference[]{International Conference on Embedded Software (EMSOFT)}{Oct}{2019}
\acmBooktitle{ACM SIGBED International Conference on Embedded Software, October 13--18, 2019, New York, NY}
%\acmPrice{15.00}
%\acmDOI{10.1145/1122445.1122456}
%\acmISBN{978-1-4503-9999-9/18/06}

%
% These commands are for a JOURNAL article.
%\setcopyright{acmcopyright}
%\acmJournal{TOG}
%\acmYear{2018}\acmVolume{37}\acmNumber{4}\acmArticle{111}\acmMonth{8}
%\acmDOI{10.1145/1122445.1122456}

%
% Submission ID. 
% Use this when submitting an article to a sponsored event. You'll receive a unique submission ID from the organizers
% of the event, and this ID should be used as the parameter to this command.
%\acmSubmissionID{123-A56-BU3}

%
% The majority of ACM publications use numbered citations and references. If you are preparing content for an event
% sponsored by ACM SIGGRAPH, you must use the "author year" style of citations and references. Uncommenting
% the next command will enable that style.
%\citestyle{acmauthoryear}

%
% end of the preamble, start of the body of the document source.
\begin{document}

%
% The "title" command has an optional parameter, allowing the author to define a "short title" to be used in page headers.
\title[Aggregation Strategies in Reachable Set Computation]{Aggregation Strategies in Reachable Set Computation\\ of Hybrid Systems}

%
% The "author" command and its associated commands are used to define the authors and their affiliations.
% Of note is the shared affiliation of the first two authors, and the "authornote" and "authornotemark" commands
% used to denote shared contribution to the research.
%\author{Ben Trovato}
%\authornote{Both authors contributed equally to this research.}
%\email{trovato@corporation.com}
%\orcid{1234-5678-9012}
%\author{G.K.M. Tobin}
%\authornotemark[1]
%\email{webmaster@marysville-ohio.com}
%\affiliation{%
%  \institution{Institute for Clarity in Documentation}
%  \streetaddress{P.O. Box 1212}
%  \city{Dublin}
%  \state{Ohio}
%  \postcode{43017-6221}
%}
%
%
%
% By default, the full list of authors will be used in the page headers. Often, this list is too long, and will overlap
% other information printed in the page headers. This command allows the author to define a more concise list
% of authors' names for this purpose.
%\renewcommand{\shortauthors}{Trovato and Tobin, et al.}

%
% The abstract is a short summary of the work to be presented in the article.
\begin{abstract}
  Computing the set of reachable states is a widely used technique for proving that a hybrid system satisfies its safety specification.
  %
  Flow-pipe construction methods interleave phases of computing continuous successors and phases of computing discrete successors.
%   are computed.
  %
  Directly doing this leads to a combinatorial explosion problem, though, as with each discrete successor there may be an interval of time
  where the transition can occur, so that the number of paths becomes exponential in the number of discrete transitions.
  %
  For this reason, most reachable set computation tools implement some form of set aggregation for discrete transitions, such as performing a
  template polyhedron or convex hull aggregation.
  %
  These aggregation methods, however, in theory can lead to unbounded error, and in practice are often
  the root cause of why a safety specification cannot be proven.

%$~~$
  This paper proposes techniques for improving the accuracy of the aggregation operations performed for reachable set computation.
  %
  First, we present two aggregation strategies over generalized stars, namely convex hull aggregation and template based aggregation.
  %
  Second, we perform adaptive deaggregation using a data structure called Aggregated Directed Acyclic Graph (AGGDAG).
  %
  Our deaggregation strategy is driven by counterexamples and hence has soundness and relative completeness guarantees.
  %
  We demonstrate the computational benefits of our approach through \new{two case studies involving satellite rendezvous and gearbox meshing}.
\end{abstract}

%
% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
% Please copy and paste the code instead of the example below.
%

%
% Keywords. The author(s) should pick words that accurately describe the work being
% presented. Separate the keywords with commas.
%\keywords{datasets, neural networks, gaze detection, text tagging}
\keywords{Hybrid Systems \and Reachable Set \and Linear Differential Equations \and Aggregations for Reachable Set \and Adaptive Deaggregation.}


%
% A "teaser" image appears between the author and affiliation information and the body 
% of the document, and typically spans the page. 

%
% This command processes the author and affiliation and title information and builds
% the first part of the formatted document.
\maketitle

%
%
%

\input{introduction}
\input{preliminaries}
\input{algorithm}
\input{casestudy}

\section{Conclusions}
%\vspace{-0.4cm}
In this paper we have focused on computing accurate reachable set computation of hybrid automata where there is high nondeterminism in the discrete transitions. We presented two common techniques used for aggregation and highlighted the relative merits and demerits of each technique. We also presented aggdag data structure and outlined the deaggregation strategies that were implemented. Using the techniques we were able to handle a challenging case study of satellite rendezvous mission and prove the passive safety property.

Handling discrete transitions is still a major hurdle in scalable and accurate computation of reachable set for linear hybrid systems. As a part of future work, we intend to explore intelligent aggregation and deaggregation strategies that adapt based on the dynamics to provide an accurate reachable set.


\bibliographystyle{ACM-Reference-Format}
\bibliography{bibfile}


\end{document}
