% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
%\documentclass[runningheads]{llncs}
%\documentclass[format=sigconf, authordraft=true]{acmart}

%
% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}

%
% \BibTeX command to typeset BibTeX logo in the docs


%
%\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

%\include{psd-macros}
%\include{psd-macros-extra}

%\usepackage{booktabs}
%\usepackage{tabularx}
%\usepackage{colortbl}
%\usepackage{xcolor}

%\usepackage[boxed,linesnumbered,lined,commentsnumbered]{algorithm2e}


\begin{document}
%

%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
%%%%
%\author{Stanley Bak\inst{1} \and
%Parasara Sridhar Duggirala\inst{2}}
%%%%%
% 
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
%\institute{Safe Sky Analytics, LLC, USA. \\ \email{stanleybak@gmail.com} \and
%Department of Computer Science, \\ University of North Carolina at Chapel Hill, USA. \\
%\email{psd@cs.unc.edu}}
%%%%%%%%
% \\
% \url{http://www.springer.com/gp/computer-science/lncs} \and
% ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
% \email{\{abc,lncs\}@uni-heidelberg.de}
%
%\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Reachable set computation tools for hybrid systems approximate the reachable set over an interval of time with a symbolic representation. 
Most reachable set computation tools implement some form of aggregation for handling discrete transitions. Sometimes, the reachable set is insufficient for inferring the safety specification since the aggregation strategies lead to very conservative overapproximations. However, if such an aggregation is not performed, then one has to keep track of exponential number of symbolic representations and incur significant computation costs. 

$~~$This paper proposes techniques for improving the accuracy of the aggregation operations performed for reachable set computation. First we present two aggregation strategies over generalized stars, namely convex hull aggregation and template based aggregation. Second, we perform adaptive deaggregation using a data structure called Aggregated Directed Acyclic Graph (AGGDAG). Our deaggregation stragety is driven by counterexamples and hence has soundness and relative completeness guarantees. We apply our technique to infer safety properties of satellite rendezvous mission and demonstrate the computational benefits of these enhancements.

%In this paper we present two types of technqiues, namely, template based and convex hull based techniques for aggregation. Additionally, we present Aggregated Directed Acyclic Graph (AGGDAG) for keeping track of reachable sets. Using AGGDAG, we present a new deaggregation technique for performing selective deaggregation. Our deaggregation strategy is guided by counterexamples and hence provides completeness guarantees for safety verification. We present a case study of inferring safety properties of satellite rendezvous and demonstrate the effectiveness of our approach.

% For handling discrete transitions, 
% One of the major challenges in computing reachable set for hybrid systems computation is to handle the discrete transitions. 

% Most reachable set computation tools implement some form of aggregation. 


\end{abstract}

%\keywords{Hybrid Systems \and Reachable Set \and Linear Differential Equations \and Aggregations for Reachable Set \and Adaptive Deaggregation.}


%
%
%

%\input{introduction}
%\input{preliminaries}
%\input{algorithm}
%\input{casestudy}

%\vspace{-0.2cm}
\section{Conclusions}
%\vspace{-0.4cm}
In this paper we have focused on computing accurate reachable set computation of hybrid automata where there is high nondeterminism in the discrete transitions. We presented two common techniques used for aggregation and highlighted the relative merits and demerits of each technique. We also presented aggdag data structure and outlined the deaggregation strategies that were implemented. Using the techniques we were able to handle a challenging case study of satellite rendezvous mission and prove the passive safety property.

Handling discrete transitions is still a major hurdle in scalable and accurate computation of reachable set for linear hybrid systems. As a part of future work, we intend to explore intelligent aggregation and deaggregation strategies that adapt based on the dynamics to provide an accurate reachable set.


%\citestyle{acmauthoryear}
\bibliographystyle{ACM-Reference-Format}
%\bibliographystyle{acm}
\bibliography{bak}

\end{document}
